Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2019-09-25 manuscript/manuscript.Rmd
tidied up folders

#PACS: 
#- PAC1
#- superPAC

MSC:
- MSC code 1
- MSC code 2

@@

bibliography: bibliography.bib
output: rticles::springer_article

---

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
```
# Introduction

Fifteen studies were included in this systematic review (Figure 1). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

```{r fig-1, fig.align="center",fig.cap="PRISMA Flow Diagram", echo=FALSE}
prsm <- PRISMAstatement::flow_exclusions(
  incl_counts = c(129, 94, 23, 15),
  total_label = "References imported for screening",
  incl_labels = c("Studies screened", "Full-text assessed for eligibility", "Included"),
  excl_labels = c("Duplicates removed", "Excluded", "Full-text excluded"),
               width = 200, height = 200)
tiff("figure-one.tiff", width=7.5, height=7, units='in', res=300, compression = 'lzw')
prsm
PRISMAstatement:::prisma_pdf(prsm)
```

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=1)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = sum(group$N, na.rm = T)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m, "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve)
out
}
```

@@

>The characteristics of each study are in online supplementary [file 1](link to file 1).

The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r format(low_risk$Measurements, scientific=F)` paired measurements (two studies did not report the total number of measurements included in their analysis). The third group compared zero-heat-flux to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements. The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements. The fifth group compared ZHF to nasopharyngeal temperature measurements and included 4 (13%) comparisons from  4 (25%) studies, and enrolled 297 participants with 109,819 paired measurements. The sixth group compared ZHF to sublingual temperature measurement and included 2 (7%) comparisons from  2 (13%) studies, and enrolled 107 participants with 22731 paired measurements. The studies included in this systematic review evaluated a ZHF temperature monitoring system manufactured by 3M. Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to as the Bair Hugger Temperature Monitoring System. All comparisons reported adherence to the ZHF device manufacturer instructions and placed the sensor on the forehead of the participants. High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies. In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.

@@

>>>>

@@

bibliography: bibliography.bib
output: rticles::springer_article
---

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
library(knitr)
```

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=1)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m, "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve)
out
}
```

@@

# Introduction

@@

Fifteen studies were included (Figure 1). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
library(ggplot2)
  library(tibble)
  library(tidyverse)
  library(ggfittext)

  line_size <- 0.50
  box_type <- "round"
  box_lines <- 0.5
  box_colour <- "#ff4f14"
  box_fill <- "white"
  text_colour <- "#ff4f14"
  arrow_colour <- "#ff4f14"

  retrieved <- 129
  duplicates <- 35
  screened <- retrieved-duplicates
  full_text <- 21
  screen_excluded <- screened-full_text
  included <- 15
  full_text_excluded <- full_text-included
  wrong_intervention <- 4
  wrong_comparator <- 2
  wrong_design <- 1
  awaiting_classification <- 2

# Main flow y coordinates  
  import_y_max <- 100
  import_y_min <- 90
  screen_y_max <- 80
  screen_y_min <- 70
  full_y_max <- 60
  full_y_min <- 50
  included_y_max <- 40
  included_y_min <- 30

# Scondary flow y coordinates  
  duplicates_y_max <- 90
  duplicates_y_min <- 80

  full_excluded_y_min <- 25
  full_excluded_y_max <- 45

  screen_excluded_y_min <- 65
  screen_excluded_y_max <- 75

  awaiting_classification_y_min <- 50
  awaiting_classification_y_max <- 60

# x coordinates  
  main_x_min <- 20
  main_x_max <- 70

  second_x_min <- 75
  second_x_max <- 95

  arrow_x <- 45

  ###Plot space set-up####
  data <- tibble(x= 23:100, y = 23:100)
   data %>% 
    ggplot(aes(x, y)) +
    theme_linedraw() +

  ########## Main box flow ###########

  # import box

  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
                  label= glue::glue(retrieved, ' references identified'), 
                  reflow = TRUE, colour = text_colour) +

# screen box
  annotation_custom(grob = grid::roundrectGrob(gp = 
                    grid::gpar(col = box_colour, fill = box_fill)),
                    xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, 
                    ymax=screen_y_max) +
  geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, ymax=screen_y_max,
           label= glue::glue(screened, ' titles and abstracts screened'), 
           reflow = TRUE, colour = text_colour) +

# full text box
  annotation_custom(grob = grid::roundrectGrob(gp = 
          grid::gpar(col = box_colour, fill = box_fill)),
          xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max) +
  geom_fit_text( xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max,
                 label= glue::glue(full_text, ' full-text articles assessed'), 
                  reflow = TRUE, colour = text_colour) +

# included box 
  annotation_custom(grob = grid::roundrectGrob(gp = 
               grid::gpar(col = box_colour, fill = box_fill)),
               xmin = main_x_min, xmax=main_x_max, 
                    ymin=included_y_min, ymax=included_y_max) +
  geom_fit_text(xmin = main_x_min, xmax=main_x_max, 
                ymin=included_y_min, ymax=included_y_max,
                label= glue::glue(included, ' studies included'), 
                 reflow = TRUE, colour = text_colour) +

######### Secondary flow boxes ############

  annotation_custom(grob = grid::roundrectGrob(gp = 
        grid::gpar(col = box_colour, fill = box_fill)),
        xmin = second_x_min, xmax=second_x_max, 
                    ymin=duplicates_y_min, ymax=duplicates_y_max) +
  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                ymin=duplicates_y_min, ymax=duplicates_y_max,
                label= glue::glue(duplicates, ' duplicates removed'),
                 reflow = TRUE, colour = text_colour) +

# excluded box 
 annotation_custom(grob = 
                              grid::roundrectGrob(gp = 
                              grid::gpar(col = box_colour, fill = box_fill)),
                            xmin = second_x_min, xmax=second_x_max, 
                    ymin=screen_excluded_y_min, ymax=screen_excluded_y_max) +
  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                ymin=screen_excluded_y_min, ymax=screen_excluded_y_max,
                label= glue::glue(screen_excluded, ' studies excluded'),
                 reflow = TRUE, colour = text_colour) +

# awaiting classifications box 
    annotation_custom(grob = 
                        grid::roundrectGrob(gp = 
                                              grid::gpar(col = box_colour, fill = box_fill)),
                      xmin = second_x_min, xmax=second_x_max, 
                      ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max) +
    geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                  ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max,
                  label= glue::glue(awaiting_classification, ' studies awaiting classification'),
                  reflow = TRUE, colour = text_colour) +

# full text excluded box 
annotation_custom(grob = 
                             grid::roundrectGrob(gp = 
                            grid::gpar(col = box_colour, fill = box_fill)),
                           xmin = second_x_min, xmax=second_x_max, 
                   ymin=full_excluded_y_min, ymax=full_excluded_y_max) +
 geom_fit_text(xmin = second_x_min, xmax=second_x_max,
                ymin=full_excluded_y_max-7, ymax=full_excluded_y_max,
                label= glue::glue(full_text_excluded, ' studies excluded'),
                 reflow = TRUE, colour = text_colour) +
 geom_fit_text(xmin = second_x_min, xmax=second_x_max,
                ymin=full_excluded_y_max-17, ymax=full_excluded_y_max-7,
                label= glue::glue(wrong_intervention, ' wrong intervention','\n',
                                  wrong_intervention, ' wrong comparator','\n',
                                  wrong_intervention, ' wrong design'),
                 colour = text_colour, grow = TRUE) +

####### Main flow arrows#######

  # Import - screen
 geom_segment(
  x=arrow_x, xend = arrow_x, y = import_y_min, yend = screen_y_max+0.25, 
  size = line_size,  colour = arrow_colour,
  arrow = arrow(length = unit(2, "mm"), type= "closed")) +

# Screen - full text
  geom_segment(
    x=arrow_x, xend=arrow_x, y=screen_y_min, yend=full_y_max+0.25, 
    size = line_size,  colour = arrow_colour,
    arrow = arrow(length = unit(2, "mm"), type= "closed")) +

# Full text - included

  geom_segment(
    x=arrow_x, xend=arrow_x, y=full_y_min, yend=included_y_max+0.25, 
    size = line_size,  colour = arrow_colour,
    arrow = arrow(length = unit(2, "mm"), type= "closed")) +

####Secondary flow arrows########

# Import - duplicates

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = duplicates_y_max,  yend = duplicates_y_max-5, linetype = "dashed",
    curvature = 0.1, colour = arrow_colour) +

# Screen - excluded

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = screen_y_min,  yend = screen_excluded_y_max-5, linetype = "dashed",
    curvature = 0.1, colour = arrow_colour) +

# Screen - awaiting

    geom_curve(
      x = arrow_x, xend = second_x_min, 
      y = screen_y_min,  yend = awaiting_classification_y_max-5, linetype = "dashed",
      curvature = -0.2, colour = arrow_colour) +

  # Full text - excluded

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = full_y_min, yend = full_excluded_y_max-10, linetype = "dashed",
    curvature = -0.2, colour = arrow_colour) +

 theme_void() +
  coord_cartesian(ylim = c(23,100))
```

The characteristics of included studies can be viewed [here](link to shiny app). The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis). There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants. Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants. Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Measurements` participants. Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.

All studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M. Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to commercially as the Bair Hugger Temperature Monitoring System. All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants. One included study also reported results for a comparison where the zero-heat-flux thermometer was placed on the forehead. We did not included this comparison in our meta-analysis.

High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies. In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.

### 2019-09-25 manuscript/manuscript.tex
tidied up folders

\author{  Aaron Conway \and  }

@@

\institute{
        Aaron Conway \at
     Peter Munk Cardiac Centre, UHN \& Lawrence S. Bloomberg Faculty of
 Nursing, University of Toronto \\
     \email{\href{mailto:aaron.conway@utoronto.ca}{\nolinkurl{aaron.conway@utoronto.ca}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

Fifteen studies were included in this systematic review (Figure 1). Two
studies reported only in abstract form were not included and assigned as
`studies awaiting classification' because there was insufficient
information provided.

@@

{\centering \includegraphics{zhf_manuscript_files/figure-latex/fig-1-1}

@@

\begin{quote}
The characteristics of each study are in online supplementary
\href{link\%20to\%20file\%201}{file 1}.
\end{quote}

The primary comparison of zero-heat-flux versus core temperature
measurements (eg, arterial, bladder, esophageal or rectal) consisted of
19 comparisons from 13 individual studies. In total, data from 576
participants with 179821 paired measurements were included in this
comparison (two studies did not report the total number of measurements
included in their analysis). The sensitivity analysis for the primary
comparison with only studies that were judged as low risk of bias across
all domains included 10 comparisons from 5 studies that enrolled 273
participants with 104294 paired measurements (two studies did not report
the total number of measurements included in their analysis). The third
group compared zero-heat-flux to core temperature measurements in ICU
patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
enrolled 246 participants with 155,598 paired measurements. The fourth
group compared ZHF to core temperature measurement in intraoperative
patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
enrolled 464 participants with 24,223 paired measurements. The fifth
group compared ZHF to nasopharyngeal temperature measurements and
included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
participants with 109,819 paired measurements. The sixth group compared
ZHF to sublingual temperature measurement and included 2 (7\%)
comparisons from 2 (13\%) studies, and enrolled 107 participants with
22731 paired measurements. The studies included in this systematic
review evaluated a ZHF temperature monitoring system manufactured by 3M.
Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
device is now referred to as the Bair Hugger Temperature Monitoring
System. All comparisons reported adherence to the ZHF device
manufacturer instructions and placed the sensor on the forehead of the
participants. High risk of bias was associated with patient selection
for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
ZHF measurements being taken with knowledge of the comparator
measurements and vice versa) and participant flow for 13 (43\%) studies.
In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
a conflict of interest or receipt of funding or equipment from the
manufacturer of the ZHF device under evaluation.

>>>>

\author{  Aaron Conway \and  Navpreet Kamboj \and  }

@@

\institute{
        Aaron Conway \at
     Peter Munk Cardiac Centre, UHN \& Lawrence S. Bloomberg Faculty of
 Nursing, University of Toronto \\
     \email{\href{mailto:aaron.conway@utoronto.ca}{\nolinkurl{aaron.conway@utoronto.ca}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Navpreet Kamboj \at
     Lawrence S. Bloomberg Faculty of Nursing, University of Toronto \\
     \email{\href{mailto:navpreet.kamboj@mail.utoronto.ca}{\nolinkurl{navpreet.kamboj@mail.utoronto.ca}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

Fifteen studies were included (Figure 1). Two studies reported only in
abstract form were not included and assigned as `studies awaiting
classification' because there was insufficient information provided.

@@

{\centering \includegraphics{fig-1-1}

@@

The characteristics of included studies can be viewed
\href{link\%20to\%20shiny\%20app}{here}. The primary comparison of
zero-heat-flux versus core temperature measurements (eg, arterial,
bladder, esophageal or rectal) consisted of 19 comparisons from 13
individual studies. In total, data from 576 participants with 179,821
paired measurements were included in this comparison (two studies did
not report the total number of measurements included in their analysis).
The sensitivity analysis for the primary comparison with only studies
that were judged as low risk of bias across all domains included 10
comparisons from 5 studies that enrolled 273 participants with 104,294
paired measurements (two studies did not report the total number of
measurements included in their analysis). There were 5 studies that
compared zero-heat-flux to core temperature measurements in ICU
patients, comprising 7 comparisons with 155,598 measurements from 246
participants. Another 9 studies were included that compared
zero-heat-flux to core temperature measurements in patients undergoing
surgery, comprising 13 comparisons with 24,223 measurements from 433
participants. Nasopharyngeal thermometers were used as the comparator
devices in 4 studies, with 109,819 paired measurements from 109,819
participants. Sublingual thermometers were used as the comparator
devices in 2 studies that reported 22,731 paired measurements from 107
participants.

All studies included in this systematic review evaluated the
zero-heat-flux temperature monitoring system manufactured by 3M.
Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
device is now referred to commercially as the Bair Hugger Temperature
Monitoring System. All comparisons reported adherence to the
zero-heat-flux device manufacturer instructions and placed the sensor on
the forehead of the participants. One included study also reported
results for a comparison where the zero-heat-flux thermometer was placed
on the forehead. We did not included this comparison in our
meta-analysis.

High risk of bias was associated with patient selection for 13 (43\%)
comparisons from 9 (56\%) studies, conduct of ZHF and comparator
measurements in 10(33\%) comparisons from 8 (50\%) studies and 12 (40\%)
comparisons 9 (30\%) studies, respectively (mostly due to ZHF
measurements being taken with knowledge of the comparator measurements
and vice versa) and participant flow for 13 (43\%) studies. In 19 (50\%)
comparisons from 8 (50\%) studies, the authors had declared a conflict
of interest or receipt of funding or equipment from the manufacturer of
the ZHF device under evaluation.
